### 2024-06-05 Scripts/Manuscript_scripts.Rmd
Update Manuscript_scripts.Rmd

```{r Fig S1c}
df_concentration <- read.csv(r'(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\head-to-head_comparisons-DNA_concentration.csv)')
df_concentration$Concentration  <- log10(df_concentration$Concentration + 1)
df_concentration$Method <- factor(df_concentration$Method,levels =c('CMEM','Power Water','AllPrep DNA') )
my_comparisons <- list(c('CMEM','Power Water'),c('CMEM','AllPrep DNA'),c('Power Water','AllPrep DNA'))
p_concentration <- ggboxplot(df_concentration, "Method", "Concentration",
          color = "Method", palette =c("#00AFBB", "#E7B800", "#FC4E07"),
          add = "jitter",add.params = list(size = 1.5, alpha = 0.5))  +
  stat_boxplot(geom = "errorbar",width=0.05,color=c("#00AFBB", "#E7B800", "#FC4E07"))  +
  stat_compare_means(comparisons = my_comparisons,label = "p.label",size=8,vjust=0) +
  scale_x_discrete(labels= c('CMEM','Power Water','AllPrep DNA')) + 
  labs(x=NULL,y='DNA concentration (log10, ng/ul)',) + #ylim(-1,10) +
  theme_bw(base_size = 24)

@@

>>>>

```{r Fig S1c}

df_concentration <- read.csv(r'(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\head-to-head_comparisons-DNA_concentration.csv)')
df_concentration$Concentration  <- log10(df_concentration$Concentration + 1)
df_concentration$Method <- factor(df_concentration$Method,levels =c('CMEM','Power Water','AllPrep DNA') )
my_comparisons <- list(c('CMEM','Power Water'),c('CMEM','AllPrep DNA'),c('Power Water','AllPrep DNA'))
p_concentration <- ggboxplot(df_concentration, "Method", "Concentration",
          color = "Method", palette =c("#00AFBB", "#E7B800", "#FC4E07"),
          add = "jitter",add.params = list(size = 1.5, alpha = 0.5))  +
  stat_boxplot(geom = "errorbar",width=0.05,color=c("#00AFBB", "#E7B800", "#FC4E07"))  +
  stat_compare_means(comparisons = my_comparisons,label = "p.label",size=8,vjust=0) +
  scale_x_discrete(labels= c('CMEM','Power Water','AllPrep DNA')) + 
  labs(x=NULL,y='DNA concentration (log10, ng/ul)',) + #ylim(-1,10) +
  theme_bw(base_size = 24)

@@

```{r Fig S1e}
df_profiles_vegan  <-  read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\microbial_profile-feasibility_validation.csv)",header = TRUE)
metadata = read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\metadata-microbial_profile-feasibility_validation.csv)",header = TRUE)

df_profiles_vegan_abundance <- df_profiles_vegan[,3:ncol(df_profiles_vegan)]
df_profiles_vegan_matrix <- as.matrix(df_profiles_vegan[,3:ncol(df_profiles_vegan)])

abundance <- select(df_profiles_vegan,-c(SampleID,Group))
rownames(abundance) <- df_profiles_vegan[1:nrow(df_profiles_vegan),1]
abundance <- t(abundance) #transposed dataframe

pca_metadata <- data.frame(df_profiles_vegan[1:nrow(df_profiles_vegan),2])
rownames(pca_metadata) <- df_profiles_vegan[1:nrow(df_profiles_vegan),1]
colnames(pca_metadata) <- c('Group')
p <- pca(abundance,metadata=pca_metadata)

# adonis test 
set.seed(123)
adonis2(df_profiles_vegan_matrix ~ Group, df_profiles_vegan, method = "bray", permutations = 999)

df_pca_output <- as.data.frame(p$rotated)
df_pca_output$SampleID <- rownames(df_pca_output)
df_pca_output <- merge(df_pca_output, metadata, by = "SampleID")

ggscatter(df_pca_output, x = "PC1", y = "PC2", color = "Group", palette = c("#0466AB", "#D15D4E"), 
           size =5, alpha = 1) +
  geom_line(data = df_pca_output, aes(group = Order), color = "black",alpha = 0.8) +
  # stat_ellipse(aes(color = Group), geom = "path", alpha = 1, linetype = "solid",linewidth =0.8,
  #              level = 0.9) + theme_pubr(border = T)
  stat_ellipse(aes(fill = Group), geom = "polygon", linetype = "solid", level = 0.95,alpha=0.3) +
#   scale_fill_manual(values = c("#0466AB", "#FFEFF2"))
  theme_pubr(base_size = 23,border = T)

```{r Fig S1f}
